Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-18 PAPER.tex
fixed sqrt(p_e)*sqrt(p_x) in large injection description
updated plots and captions with latest sigloss runs

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e. in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal).  However it is useful as a check of our system in a relatively simple case. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term. Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.png}
	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper 
limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
estimates agree (the analytic curve should encompass $95\%$ of the points).}
	\label{fig:ps_noise}
\end{figure*}

>>>>

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e. in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal).  However it is useful as a check of our system in a relatively simple case. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term. Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.png}
	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The original weighted 
power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation. The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper 
limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
estimates agree.}
	\label{fig:ps_noise}
\end{figure*}
